The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-20 Writeup/paper_v3.tex
Many points discussed implemented

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited_withcoil}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} and~\ref{E:pz2} with best fit
    parameters are plotted over it. 
           Lower panel: Plot of $\delta_{g,\text{1D}} =
           N/N_{\text{mod}}-1$ with each functional form as the model
           for each redshift bin. \arun{Note to self: Give parameter values.}
\rachel{How does this figure look if you show the plot range with the
  histogram going to $z=0$ (still only fitting to $0.3<z<1.25$)?  It
  might be nicer to do that and put a vertical line at $z=0.3$ to
  remind the reader that you only fit above that redshift.}
}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity. The figures show chi-squared and gamma functions fitted to the histogram \citep{Redshift_modelling}.
For our (flux-limited) sample of galaxies, up to $z=1.0~(1.25)$
(\rachel{fix this to the correct one once we make final decisions}), we fit
parametric models to the histograms of photometric redshifts in order
to assign values of overdensity.  We choose our bins to be $0.05$ wide
starting from $z=0.3$, where the bin width is selected to be somewhat
larger than the photometric redshift error but narrow enough that we
can still identify rather than averaging over real cosmological
structures.  We neglect the lowest
redshifts which have negligible cosmological volume and where the
galaxy population tends to be intrinsically bright and large enough
that a non-negligible fraction is lost due to the cuts we impose
(Sec.~\ref{S:data}).

The parametric redshift distributions that we use are
\begin{equation}\label{E:pz1}
 p_1(z) \propto z^{a-1}\exp\left[{-bz}\right]
\end{equation}
and 
\begin{equation}\label{E:pz2}
 p_2(z) \propto z^2\exp{\left[-\left(\frac{z}{z_0}\right)^{1.5}\right]},
\end{equation}
the latter of which was first presented by
\cite{Redshift_modelling}. Here $a$, $b$, and
$z_0$ are free parameters that are to be determined.  The
normalization constants depend not only on the parameters but also on
the lower and the upper limit of the redshifts considered, where we
fix the normalization to ensure that the predicted number of galaxies
in the range used ($0.3<z<1$) is equal to the actual number. 
Fig.~\ref{fig:redshift_fluxlimited} shows the photometric redshift
histogram together with the best-fitting parametric distributions.
\rachel{New suggestion re: 2nd redshift distribution: it just looks so
  bad, I worry that this functional form is simply wrong 
  and we should use something newer that has been shown to work with
  modern redshift surveys.  Let me suggest something you can
  do as an immediate sanity check.   Look at
  \cite{2004ApJ...617..765C} table 4, which gives parametrized fits to
  the redshift distribution from DEEP2 for samples binned by
  $R_\text{AB}$ and $I_\text{AB}$.  Use the results for the
  $18<I_\text{AB}<23$ bin and the $18<I_\text{AB}<24$ bin,
  interpolating linearly between them since your sample is limited at
  $23.5$.  Their results suggest that either $z^2 \exp{[-z/0.262]}$ or
  $z^2 \exp{[-(z/0.361)^{1.2}]}$ should be decent descriptions of your sample.  Just as a quick
  sanity check can you please plot those  distributions (appropriately
  normalized) on top of what you have in the top panel of figure 1,
  and see how they look?  If they look OK, then I would be inclined to
  completely eliminate the 2nd distribution, and just use the 1st one
  that you're fitting and one of the ones from Coil as your way of
  checking overdensities and underdensities.
}

The estimated overdensity in a redshift bin is defined by comparing
the observed galaxy counts in the bin with the counts that are
predicted in that bin by one of the models in Eqs.~\eqref{E:pz1}
and~\eqref{E:pz2}:
\begin{equation}
\delta_{g,\text{1D}}=\frac{(N-N_{\text{mod}})}{N_{\text{mod}}},
\end{equation}
where
\begin{equation}
N_\text{mod} = \int_{z_\text{min}}^{z_\text{max}} p(z) \,\mathrm{d}z
\end{equation}
is determined by integrating the redshift distribution within the
limits of that redshift slice. 
%(\rachel{This $\delta$ definition is important, so it should be in an equation environment.})
Note that $\delta_{g,\text{1D}}$ is dependent on our choice of model
redshift distribution, and should have a mean value of $0$ over the
entire redshift range. % If a model and the distribution agree, then $\delta_{g,\text{1D}}=0$ for that model at all the redshifts.

@@

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Finally, we can circumvent the problem of redshift evolution of the
luminosity by imposing cuts on stellar mass instead. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limits.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which
includes COSMOS. They considered for this work a single stellar
population (\rachel{What do you mean by a single stellar population?})
following a Chabrier IMF \citep{ChabrierIMF}. 
We plot their SMF for \emph{all} galaxies in Fig.~\ref{fig:smf} for
reference. Their SMF is higher than ours since they reach a $K_s$-band
$5\sigma$ depth of 24.9. 
As for $M_I$, we compare the stellar mass function in the $m_\text{F814W}\le23.5$ sample with that in the $m_\text{F814W}\le25.2$ sample. 
The sample with $\log(M/M_\odot) > 10.15$ is $\sim 95$ per cent
complete in the redshift bin $0.75 \le z< 0.85$ and has 10~341
galaxies in total across all redshifts.
Thus, we construct a third volume-limited sample \s$3$ by imposing the stellar mass cut mentioned above. The number of galaxies in redshift slices
are tabulated in Table~\ref{table:GalaxyCounts} for all three ways
discussed in this section for obtaining a volume-limited sample. The
stellar-mass limited sample is the smallest, most likely because when
converting from flux to stellar mass, the stellar mass-to-light ratios
vary strongly with galaxy type, so red galaxies with high $M_*/L$
simply have too low a flux compared to the blue galaxies at the same
$M_*$, and are not observed.

@@

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_vollimited_withcoil}
  \caption{
Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$)
\s$1$ sample with photometric redshift bins that are 0.05 wide. Two
analytical functions with best fit parameters are plotted over it. 
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
           N/N_{\text{mod}}$ with each functional form as the model
           for each redshift bin. \rachel{I am quite concerned that
             something has gone wrong with this fit (in the sense that
           there may be a bug).  Why is the redshift distribution
           shown in blue forced to zero at $z=0.3$?  It should go to
           zero at $z=0$, not $0.3$.  It is clearly not normalized to the same total number as the redshift histogram, either.  In terms of formatting, please
           implement the same changes that I suggested for the
           flux-limited sample redshift distribution plot.}}
  \label{fig:redshift_vollimited}
\end{figure}

@@

\rachel{I think it would be useful to take the entire sample that we
  use for science, and show the overall distributions of axis ratio,
  distortion (one curve for Claire's and one curve for
  re-Gaussianization), \sersic index, and \btt.  This would be a
  nearly full-page four panel figure, but I think it's worthwhile to
  illustrate the nature of the sample.  For example, it will clearly
  show why we cannot use the distributions of \sersic index and \btt,
  because of the hard cutoffs.}

@@

\begin{table}
 \centering
 \begin{tabular}[\columnwidth]{ | l | c | c | c | }
  \hline
  %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
  Redshift bins & \s$1$ & \s$2$ & \s$3$ \\
  \hline
  All overdense vs.  & \scinot{1.1}{-4} & \scinot{2.6}{-5} & \scinot{1.9}{-6} \\
  All underdense     & \scinot{1}{-5} & $<\scinot{1}{-5}$ & $<\scinot{1}{-5}$ \\ \hline 
  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & 0.61 & 0.43 & 0.23 \\
  $[0.80,0.85]$ (OD) & 0.49 & 0.24 & 0.13 \\ \hline
  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & \scinot{5.8}{-4} & \scinot{1.5}{-5} & \scinot{3.5}{-6} \\
  $[0.55,0.65]$ (UD) & \scinot{9.8}{-4} & $<\scinot{1}{-5}$ & $<\scinot{1}{-5}$ \\ \hline
 \end{tabular}
 \caption{$p$-values from the Kolmogorov-Smirnov (top) and
   Anderson-Darling (bottom) tests obtained by comparing the
   distributions of axis ratios for three cases: \emph{all} overdense
   (OD) vs. \emph{all} underdense (UD), two overdense bins that are
   not very separated in redshift, and a pair of adjacent overdense
   and underdense bins. \s$1$, \s$2$, \s$3$ refer to the three
   different types of volume-limited samples.
          The Anderson-Darling $p$-values are correct only up to 5
          decimal places. 
\rachel{What does this last sentence mean?  Why?  I think you need
  clarification of this point in this table and the next one.
\arun{I meant, R computes the p-values only upto 5 decimal places. This is why it is written as \scinot{1}{-5} and not as \scinot{1.0}{-5} }}
% \rachel{What are the 0 entries in this and other tables?  Just how close to zero are they?  Since 0 is not really achieve, I recommend defining a value (such as $10^{-10}$ below which you will just say $<10^{-10}$ and give the value if it's above that, even if it seems really small to you, like $10^{-8}$.  Also, say $1.1\times 10^{-4}$ rather than $1.1e-4$.}
          }
 \label{table:pvalues_all}
\end{table}

\begin{table}
 \centering
 \begin{tabular}[\columnwidth]{ | l | c | c | c | }
  \hline
  %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
  Redshift bins & \s$1$ & \s$2$ & \s$3$ \\
  \hline
  All overdense vs. & \scinot{5.6}{-4} & \scinot{1.0}{-4} & \scinot{3.3}{-6} \\
  All underdense    & \scinot{3}{-5} & \scinot{1}{-5} & $<\scinot{1}{-5}$ \\ \hline 
  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & 0.96 & 0.75 & 0.54 \\
  $[0.80,0.85]$ (OD) & 0.52 & 0.34 & 0.23 \\ \hline
  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & \scinot{6.0}{-3} & \scinot{2.5}{-4} & \scinot{2.4}{4} \\
  $[0.55,0.65]$ (UD) & \scinot{1.2}{-2} & \scinot{2.5}{-4} & \scinot{5}{-5} \\ \hline
 \end{tabular}
 \caption{$p$-values from the Kolmogorov-Smirnov (top) and
   Anderson-Darling (bottom) obtained by comparing the second
   moments-based ellipticities for three the same three cases as in
   Table~\ref{table:pvalues_all}.  \arun{Should I write only two
     significant digits for higher $p$-values?} \rachel{Yes.  The same
     comment applies to the previous table, too.}
           The Anderson-Darling $p$-values are correct only up to 5 decimal places. }
 \label{table:pvalues_momentbased_all}
\end{table}

@@

\rachel{Overall, I find it quite confusing that the underdense regions
  are red and the overdense regions are blue on all of the plots in
  this section and the section on \sersic $n$ and $B/T$.
  The underdense regions are dominated by blue galaxies and the
  overdense are dominated by red galaxies, so having the plot colors
  reversed creates some cognitive dissonance.  Can you reverse them to
  more naturally match up point color with galaxy type?} \arun{On it.}

@@

As shown in Fig.~\ref{fig:rms_ellip}, the underdense regions have  higher values for RMS ellipticities when compared to the
overdense regions. The difference between the underdense and overdense
regions for $z>0.5$ is significantly larger than any redshift
evolution across the $z>0.5$ \arun{$z<0.5$, you mean?} range.  
Our conclusions are very similar if we use the RMS distortion from Eq.~\eqref{eq:distortion} instead
of the ellipticities. (\rachel{Our statements at the low redshift end
  regarding the amount of redshift evolution will depend on whether
  we're using the solid or open points, and the text and caption do
  not say which samples they correspond to, so I was not able to
  address this in the text.  Please do that once it is your turn to edit.})

The sign of the dependence on the local environment is reasonable when
compared with previous work on the morphology-density
relation. Overdense regions typically contain many old, elliptical
galaxies which are close to round (large axis ratio and low RMS ellipticity). 
In contrast, the underdense regions typically contain a larger
population of younger, disk galaxies, which have lower axis ratios and
higher RMS ellipticity. \rachel{Important note: this argument was
  given completely backwards.  I fixed it, but please watch out for
  this in future since it's a key point behind this work.}

@@

Next, we show an analogous plot of RMS ellipticities \arun{Is this ellipticity or distortion?} for all three
volume-limited sample using the moments-based shape estimates in
Fig.~\ref{fig:rms_ellip_momentbased}. The conclusions are quite
similar to those using the shapes from the \sersic profile fits, with
the underdense regions standing out in having larger RMS distortions 
than the other redshift slices, an effect that is substantially larger
than any average redshift evolution of the RMS distortions.

@@

For the morphological parameters that we described in
Sec.~\ref{sub:axisratio}, the \sersic index and bulge-to-total ratio,
we do not compare the distributions directly.  Doing so is relatively
tricky because both distributions have hard cutoffs that are enforced
in the fitting process (\sersic $n$ in the range $[0.25, 6]$ and
$0.05<B/T<0.95$). See Fig.~\ref{fig:sample_histograms}.
The KS and AD statistical tests are both sensitive to exactly what happens at these hard boundaries in the distributions.
\arun{AD test is actually not so sensitive to the boundaries.}
So, instead of using the full distributions, we will study the
dependence of these quantities on environment by computing the median
values in different redshift slices.  Median values are preferred
over the full distributions or even the sample means since the medians
are more robust to what happens at the edges of the distributions.

@@

We now repeat the analysis with wider redshift bins. Pretending to be ignorant of any overdensities and underdensities along the line of sight, we choose the slices in redshift to be $\left[ 0.3 - 0.5 \right]$,
$\left[ 0.5 - 0.7\right]$ and $\left[ 0.7 - 0.85\right]$.
\begin{figure}
 \centering
 \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution_wide} \
 \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution_wide}
 \caption{ RMS ellipticities as a function of redshift. The horizontal errorbars indicate
           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
         }
 \label{fig:rms_ellip_wide}
\end{figure}

>>>>

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} and~\ref{E:pz2} with best fit
    parameters are plotted over it. 
           Lower panel: Plot of $\delta_{g,\text{1D}} =
           N/N_{\text{mod}}-1$ with each functional form as the model
           for each redshift bin. \arun{Note to self: Give parameter values.}
\rachel{How does this figure look if you show the plot range with the
  histogram going to $z=0$ (still only fitting to $0.3<z<1.25$)?  It
  might be nicer to do that and put a vertical line at $z=0.3$ to
  remind the reader that you only fit above that redshift.} \arun{Done.}
}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity. The figures show chi-squared and gamma functions fitted to the histogram \citep{Redshift_modelling}.
For our (flux-limited) sample of galaxies, up to $z=1.25$, we fit
parametric models to the histograms of photometric redshifts in order
to assign values of overdensity.  We choose our bins to be $0.05$ wide
starting from $z=0.3$, where the bin width is selected to be somewhat
larger than the photometric redshift error but narrow enough that we
can still identify rather than averaging over real cosmological
structures.  We neglect the lowest
redshifts which have negligible cosmological volume and where the
galaxy population tends to be intrinsically bright and large enough
that a non-negligible fraction is lost due to the cuts we impose
(Sec.~\ref{S:data}).

The parametric redshift distributions that we use are
\begin{equation}\label{E:pz1}
 p_1(z) \propto z^{a-1}\exp\left[{-z/z_1}\right]
\end{equation}
and 
\begin{equation}\label{E:pz2}
 %p_2(z) \propto z^2\exp{\left[-\left(\frac{z}{z_0}\right)^{1.5}\right]},
 p_2(z) \propto z^{b-1}\exp\left( -\frac{1}{2}\left( \frac{z}{z_2} \right)^2\right)
\end{equation}
%the latter of which was first presented by \cite{Redshift_modelling}.
Here $a$, $b$, $z_1$ and
$z_2$ are free parameters that are to be determined.  The
normalization constants depend not only on the parameters but also on
the lower and the upper limit of the redshifts considered, where we
fix the normalization to ensure that the predicted number of galaxies
in the range used ($0.3<z<1.25$) is equal to the actual number. 
Fig.~\ref{fig:redshift_fluxlimited} shows the photometric redshift
histogram together with the best-fitting parametric distributions.

We compare our fits to the fits made by \cite{2004ApJ...617..765C} for 
the DEEP2 survey. Interpolating their results for the $18<I_\text{AB}<23$
and $18<I_\text{AB}<24$ samples, we obtain that the redshift distributions 
as

\begin{equation}
 \label{E;pz3}
 p_3(z) \propto z^2 \exp{[-z/0.262]}
\end{equation}
and 
\begin{equation}
 \label{E;pz4}
 p_4(z) \propto z^2 \exp{[-(z/0.361)^{1.2}]}
\end{equation}

which are also plotted in Fig.~\ref{fig:redshift_fluxlimited}.

\rachel{New suggestion re: 2nd redshift distribution: it just looks so
  bad, I worry that this functional form is simply wrong 
  and we should use something newer that has been shown to work with
  modern redshift surveys.  Let me suggest something you can
  do as an immediate sanity check.   Look at
  \cite{2004ApJ...617..765C} table 4, which gives parametrized fits to
  the redshift distribution from DEEP2 for samples binned by
  $R_\text{AB}$ and $I_\text{AB}$.  Use the results for the
  $18<I_\text{AB}<23$ bin and the $18<I_\text{AB}<24$ bin,
  interpolating linearly between them since your sample is limited at
  $23.5$.  Their results suggest that either $z^2 \exp{[-z/0.262]}$ or
  $z^2 \exp{[-(z/0.361)^{1.2}]}$ should be decent descriptions of your sample.  Just as a quick
  sanity check can you please plot those  distributions (appropriately
  normalized) on top of what you have in the top panel of figure 1,
  and see how they look?  If they look OK, then I would be inclined to
  completely eliminate the 2nd distribution, and just use the 1st one
  that you're fitting and one of the ones from Coil as your way of
  checking overdensities and underdensities.
} \arun{The functional forms with the parameters in  \cite{2004ApJ...617..765C} agree well with the histogram and our models.}

The estimated overdensity in a redshift bin is defined by comparing
the observed galaxy counts in the bin with the counts that are
predicted in that bin by one of the models in Eqs.~\eqref{E:pz1}
and~\eqref{E:pz2}:
\begin{equation}
\delta_{g,\text{1D}}=\frac{(N-N_{\text{mod}})}{N_{\text{mod}}},
\end{equation}
where
\begin{equation}
N_\text{mod} = \int_{z_\text{min}}^{z_\text{max}} p(z) \,\mathrm{d}z
\end{equation}
is determined by integrating the redshift distribution within the
limits of that redshift slice. 
%(\rachel{This $\delta$ definition is important, so it should be in an equation environment.})
Note that $\delta_{g,\text{1D}}$ is dependent on our choice of model
redshift distribution, and should have a mean value of $0$ over the
entire redshift range. \arun{weighted by the number fraction in each bin.} % If a model and the distribution agree, then $\delta_{g,\text{1D}}=0$ for that model at all the redshifts.

@@

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Finally, we can circumvent the problem of redshift evolution of the
luminosity by imposing cuts on stellar mass instead. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limits.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which
includes COSMOS. They considered for this work a single stellar
population (\rachel{What do you mean by a single stellar population?} \arun{I had lifted that term from the paper since I thought it was important to highlight that. 
They consider those stars that have metallicity of that of the sun formed at redshift $z=5$.})
following a Chabrier IMF \citep{ChabrierIMF}. 
We plot their SMF for \emph{all} galaxies in Fig.~\ref{fig:smf} for
reference. Their SMF is higher than ours since they reach a $K_s$-band
$5\sigma$ depth of 24.9. 
As for $M_I$, we compare the stellar mass function in the $m_\text{F814W}\le23.5$ sample with that in the $m_\text{F814W}\le25.2$ sample. 
The sample with $\log(M/M_\odot) > 10.15$ is $\sim 95$ per cent
complete in the redshift bin $0.75 \le z< 0.85$ and has 10~341
galaxies in total across all redshifts.
Thus, we construct a third volume-limited sample \s$3$ by imposing the stellar mass cut mentioned above. The number of galaxies in redshift slices
are tabulated in Table~\ref{table:GalaxyCounts} for all three ways
discussed in this section for obtaining a volume-limited sample. The
stellar-mass limited sample is the smallest, most likely because when
converting from flux to stellar mass, the stellar mass-to-light ratios
vary strongly with galaxy type, so red galaxies with high $M_*/L$
simply have too low a flux compared to the blue galaxies at the same
$M_*$, and are not observed.

@@

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_vollimited_withcoil}
  \caption{
Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$)
\s$1$ sample with photometric redshift bins that are 0.05 wide. Two
analytical functions with best fit parameters are plotted over it. 
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
           N/N_{\text{mod}}$ with each functional form as the model
           for each redshift bin. \rachel{I am quite concerned that
             something has gone wrong with this fit (in the sense that
           there may be a bug).  Why is the redshift distribution
           shown in blue forced to zero at $z=0.3$?  It should go to
           zero at $z=0$, not $0.3$.  It is clearly not normalized to the same total number as the redshift histogram, either.  In terms of formatting, please
           implement the same changes that I suggested for the
           flux-limited sample redshift distribution plot.}\arun{This will change once I discuss with you.}} 
  \label{fig:redshift_vollimited}
\end{figure}

@@

\rachel{I think it would be useful to take the entire sample that we
  use for science, and show the overall distributions of axis ratio,
  distortion (one curve for Claire's and one curve for
  re-Gaussianization), \sersic index, and \btt.  This would be a
  nearly full-page four panel figure, but I think it's worthwhile to
  illustrate the nature of the sample.  For example, it will clearly
  show why we cannot use the distributions of \sersic index and \btt,
  because of the hard cutoffs.} \arun{Done.}

@@

\begin{table}
 \centering
 \begin{tabular}[\columnwidth]{ | l | c | c | c | }
  \hline
  %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
  Redshift bins & \s$1$ & \s$2$ & \s$3$ \\
  \hline
  All overdense vs.  & \scinot{1.1}{-4} & \scinot{2.6}{-5} & \scinot{1.9}{-6} \\
  All underdense     & \scinot{1}{-5} & $<\scinot{1}{-5}$ & $<\scinot{1}{-5}$ \\ \hline 
  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & 0.61 & 0.43 & 0.23 \\
  $[0.80,0.85]$ (OD) & 0.49 & 0.24 & 0.13 \\ \hline
  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & \scinot{5.8}{-4} & \scinot{1.5}{-5} & \scinot{3.5}{-6} \\
  $[0.55,0.65]$ (UD) & \scinot{9.8}{-4} & $<\scinot{1}{-5}$ & $<\scinot{1}{-5}$ \\ \hline
 \end{tabular}
 \caption{$p$-values from the Kolmogorov-Smirnov (top) and
   Anderson-Darling (bottom) tests obtained by comparing the
   distributions of axis ratios for three cases: \emph{all} overdense
   (OD) vs. \emph{all} underdense (UD), two overdense bins that are
   not very separated in redshift, and a pair of adjacent overdense
   and underdense bins. \s$1$, \s$2$, \s$3$ refer to the three
   different types of volume-limited samples.
          The Anderson-Darling $p$-values are computed only up to 5
          decimal places. 
\rachel{What does this last sentence mean?  Why?  I think you need
  clarification of this point in this table and the next one.
\arun{I meant, R computes the p-values only upto 5 decimal places. This is why it is written as \scinot{1}{-5} and not as \scinot{1.0}{-5} }}
% \rachel{What are the 0 entries in this and other tables?  Just how close to zero are they?  Since 0 is not really achieve, I recommend defining a value (such as $10^{-10}$ below which you will just say $<10^{-10}$ and give the value if it's above that, even if it seems really small to you, like $10^{-8}$.  Also, say $1.1\times 10^{-4}$ rather than $1.1e-4$.}
          }
 \label{table:pvalues_all}
\end{table}

\begin{table}
 \centering
 \begin{tabular}[\columnwidth]{ | l | c | c | c | }
  \hline
  %\parbox[t]{0.15\columnwidth}{Redshift bins} & \parbox[t]{0.15\columnwidth}{Tests} & \parbox[t]{0.15\columnwidth}{Luminosity-selected} & \parbox[t]{0.15\columnwidth}{Luminosity-selected with B-band evolution} & \parbox[t]{0.15\columnwidth}{Stellar-mass-selected} \\
  Redshift bins & \s$1$ & \s$2$ & \s$3$ \\
  \hline
  All overdense vs. & \scinot{5.6}{-4} & \scinot{1.0}{-4} & \scinot{3.3}{-6} \\
  All underdense    & \scinot{3}{-5} & \scinot{1}{-5} & $<\scinot{1}{-5}$ \\ \hline 
  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & 0.96 & 0.75 & 0.54 \\
  $[0.80,0.85]$ (OD) & 0.52 & 0.34 & 0.23 \\ \hline
  $[0.65,0.75]$ (OD) vs.$\!\!\!$ & \scinot{6.0}{-3} & \scinot{2.5}{-4} & \scinot{2.4}{4} \\
  $[0.55,0.65]$ (UD) & \scinot{1.2}{-2} & \scinot{2.5}{-4} & \scinot{5}{-5} \\ \hline
 \end{tabular}
 \caption{$p$-values from the Kolmogorov-Smirnov (top) and
   Anderson-Darling (bottom) obtained by comparing the second
   moments-based ellipticities for three the same three cases as in
   Table~\ref{table:pvalues_all}.  \arun{Should I write only two
     significant digits for higher $p$-values?} \rachel{Yes.  The same
     comment applies to the previous table, too.}
           The Anderson-Darling $p$-values are computed only up to 5 decimal places. }
 \label{table:pvalues_momentbased_all}
\end{table}

@@

\rachel{Overall, I find it quite confusing that the underdense regions
  are red and the overdense regions are blue on all of the plots in
  this section and the section on \sersic $n$ and $B/T$.
  The underdense regions are dominated by blue galaxies and the
  overdense are dominated by red galaxies, so having the plot colors
  reversed creates some cognitive dissonance.  Can you reverse them to
  more naturally match up point color with galaxy type?} \arun{Fixed.}

@@

As shown in Fig.~\ref{fig:rms_ellip}, the underdense regions have  higher values for RMS ellipticities when compared to the
overdense regions. The difference between the underdense and overdense
regions for $z>0.5$ is significantly larger than any redshift
evolution across the $z>0.5$ range.  
Our conclusions are very similar if we use the RMS distortion from Eq.~\eqref{eq:distortion} instead
of the ellipticities. (\rachel{Our statements at the low redshift end
  regarding the amount of redshift evolution will depend on whether
  we're using the solid or open points, and the text and caption do
  not say which samples they correspond to, so I was not able to
  address this in the text.  Please do that once it is your turn to edit.} 
  \arun{Convention: Open centers and thick errorbars for \s$3$ and filled centers and thin errorbars for \s$1$ and \s$2$})

The sign of the dependence on the local environment is reasonable when
compared with previous work on the morphology-density
relation. Overdense regions typically contain many old, elliptical
galaxies which are close to round (large axis ratio and low RMS ellipticity). 
In contrast, the underdense regions typically contain a larger
population of younger, disk galaxies, which have lower axis ratios and
higher RMS ellipticity. \rachel{Important note: this argument was
  given completely backwards.  I fixed it, but please watch out for
  this in future since it's a key point behind this work.} \arun{Oops, sorry. Thanks!}

@@

Next, we show an analogous plot of RMS ellipticities %\arun{Is this ellipticity or distortion?} 
for all three
volume-limited sample using the moments-based shape estimates in
Fig.~\ref{fig:rms_ellip_momentbased}. The conclusions are quite
similar to those using the shapes from the \sersic profile fits, with
the underdense regions standing out in having larger RMS distortions 
than the other redshift slices, an effect that is substantially larger
than any average redshift evolution of the RMS distortions.

@@

For the morphological parameters that we described in
Sec.~\ref{sub:axisratio}, the \sersic index and bulge-to-total ratio,
we do not compare the distributions directly.  Doing so is relatively
tricky because both distributions have hard cutoffs that are enforced
in the fitting process (\sersic $n$ in the range $[0.25, 6]$ and
$0.05<B/T<0.95$). See Fig.~\ref{fig:sample_histograms}.
The KS statistical test is sensitive to exactly what happens at these hard boundaries in the distributions.
%\arun{AD test is actually not so sensitive to the boundaries.}
So, instead of using the full distributions, we will study the
dependence of these quantities on environment by computing the median
values in different redshift slices.  Median values are preferred
over the full distributions or even the sample means since the medians
are more robust to what happens at the edges of the distributions.

@@

We now repeat the analysis with wider redshift bins. Pretending to be ignorant of any overdensities and underdensities along the line of sight, we choose the slices in redshift to be $\left[ 0.3 - 0.5 \right]$,
$\left[ 0.5 - 0.7\right]$ and $\left[ 0.7 - 0.85\right]$.
\begin{figure}
 \centering
 \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution_wide} \
 \includegraphics[width=1.0\columnwidth]{rms_ellip2_Bbandevolution_wide}
 \caption{ RMS ellipticities as a function of redshift. The horizontal errorbars indicate
           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
         }
 \label{fig:rms_ellip_wide}
\end{figure}
